\documentclass[../../../main.tex]{subfiles}

\begin{document}

\begin{comment}
- not always designed for multi user?
- not intuitive?

GS (till end): not user friendly?
shoudn't be time consuming to add data/etc
manual admin can be time consuming, try to automate
ability for mutliple concurrent users
easy and transpaancy for multi users
log in and see what was done the day before
easy to follow/read

not able to re-order items in a single place
have to go do diff platforms when ready to re-order

limited functionality
want to be able to track purchased items
as well as handle budgeting
existing solutions don't have multiple functions
so you need to duplicate information on different apps/areas
like how Monzo combines budgeting with card and tracking txns.

are these a problem with the current app or a problem you have that
you need a solution to.

is problem with current app
or need support with inventory/organisation

do more research on downsides of different alternatives/

---
Popular inventory management solutions are relatively expensive, and may be out
of reach for individuals or small schools.
Inventory systems have numerous benefits for businesses and individuals alike; a business
may choose to track their supply levels where an individual may wish to catalogue their DVD collection. \\

\noindent My goal is to create a web-based application aimed at both businesses and individuals to manage
inventory, with additional modern features such as automatic item re-ordering when stocks are running low.\\

\noindent Traditional inventory management solutions are typically single-user at best, whereas I intend to create
a multi-user, collaborative environment.\\

\noindent In my view, an inventory system should be:

\begin{outline}
    \1 Easy for end users to use.
    \1 Cross platform
    \1 Performant interface
    \1 Efficient in terms of adding data
    \1 Allow for easy cataloguing of inventory
    \1 Allow for item scanning using QR codes / barcodes
    \1 Be able to source data from external sources
    \1 Support both consumable and non-consumable goods.


\end{outline}

An inventory system should be able to:

time consuming to add data
not user friendly

- catalogue of inventory, re-order for you
- scan using a phone (no external hardware needed)
- alert / re-order when stocks are running low.
- purchase links
- stretch: source data from amazon or equivalent instead of typing it manually
- search engine for catalogued and new Parts
- provides with options for where to purchase certain goods
- button to re-order
- smart device???????
- predict when stocks will run out.
- source data from external sources
- like monzo projection of when it will run out
- how much you are spending each month on goods
- nfc support to easily scan / etc items (might be too hard on iOS)
\textbf{Barcode check in / out}
- monzo integration
- budgeting - figure projections  as well
clearly define what the APP will feature.
Think about
- potential users
- how does the app cater to their needs - different features etc


\end{comment}

Hill School is a preparatory that taking students aged 2-11. It is housed in a Victorian building
and also features an extensive playground. The library at the Hill School currently runs on a
paper-ticket system with books categorised using coloured stickers. Staff and students
borrow books weekly and often students are on waiting lists to borrow popular books. Waiting lists
are not managed by any form of digital system, instead being written in a textbook by the staff
librarian.

\noindent \\ The librarian, Mrs. Young, has suggested that her workload could be reduced if the
system was digitized.

\subparagraph{Initial Requirements\\}

\noindent \\ Mrs. Young has provided us with an initial list of requirements:

\begin{outline}
    \1 Searchable index of books.
    \1 Take and return (due) dates to be stored digitally.
    \1 Ability to view which books have been checked out.
\end{outline}

\end{document}