\documentclass[../../../main.tex]{subfiles}

\begin{document}

\paragraph{Question Set}
\begin{outline}
    \1 What would you consider your skill level to be regarding technology?
    \1 Do you currently have a way to manage inventory?
    \1 If so, what is your current solution?
    \1 What aspects of this solution do you like?
    \1 What aspects of this solution do you dislike?
    \1 What features would you \textbf{require} in a custom solution?
    \1 What features would \textbf{enhance} your experience?
\end{outline}

\begin{comment}
CF
CF "SLT": library

what is the current system?
borrowing cards and date stamps that are manually written in for when books are due back
borrower card for who borrowed which book, stickers placed on books for categories

problems with existing solution
time consuming; cards get lost; stickers fall off
not very quick to see who borrowed what; have to look through all cards


like about the existing solution
primary aged students/children can do it (themselves)

requirements for new solution

scan a barcode / borrower ticket and instantly see what they've borrowed.

cost effective
compatible with existing hardware/software
works on ipa
ability to renew
notified when books are overdue
statistics (book numbers) by genre/author/category

enhancements for new solution
colored stickers for categories
ability to charge parents (make an invoice?)

is there a specific way you would like the system to be organised?
yes, we are a library so by preset genres and categories

do you have any questions of your own?
what's the timeframe for this being completed - March.

fake pupil: Ella (no surname)
year 6 "head librarian" age 10-**11** (y6)

problems with the current system
"so old fashioned, should be able to scan using my iPad! Then it could be pupil-led."

benefits
can see who borrowed the book I want and nag them to return it so I can read it!
when I forget which book I've borrowed the teacher can easily find which books I've lost

requirements
iPads; fast (can be done in break times - borrow/renew)




fake teacher
equipment for science lab/art room/ etc


can say helping a junior school.


\end{comment}

\end{document}