\documentclass[../../../main.tex]{subfiles}

\begin{document}

\noindent From my interviews, I have found that our stakeholders are seeking a modern, digital alternative
to their paper-based record keeping in the library. The stakeholders are primarily looking for
a system to manage library books, but they have indicated that a system to manage school
resouces would also be useful. To that end, I will seek to create a singular system that can fulfill both of these requests.

\noindent \\ I will conduct some research on inventory systems and will produce a list of features based on the stakeholder's answers to incorporate into my solution.

\noindent \\ The key takeaways from the interviews were that:

\begin{outline}
    \1 The stakeholders are looking for a modern alternative to their existing solution(s)
    \1 That can be used effectively for both general inventory management as well as library book management and tracking
    \1 The solution will need to be easy to use so that children as well as those less familiar with technology can still make effective use of the system.
    \1 The solution will need to be completed by March 2024 so that the system can be deployed before the end of the current acedemic year.
\end{outline}

\noindent However, after the interview I realised two features that required further clarification from the stakeholders:

\begin{outline}
    \1 Ella would prefer the system to be accessible using a mobile device.
    \2 The other stakeholders did not indicate a preference. \\
    It is apparent that I should have asked the stakeholders this during the interview, signifying a gap in the coverage of my interview questions. \\\\
    I will continue with the assumption based on Ella's feedback that the system should be accessed from a mobile device and will ask the other stakeholders for their feedback when I propose the solution's features to them. I will gather additional feedback at this time before development of the solution begins.
    \1 The system should support multiple users.
    \2 The stakeholders did not indicate wheather they required the ability to \textbf{administer} the system, such as the ability to manage other users or perform other privileged functions.\\\\
    This would be a complex feature to implement, and we are working under a strict deadline to complete the entire system. As such, I will propose the system without this feature.\\\\
    However, due to the architecture of the designed system, it should be straightforward to implement this feature in the future. (talk more about why)

\end{outline}

\end{document}